---
title: "Final project (Statistical Inference)"
author: "Robinson Montes Gómez"
date: "11/15/2020"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PART 1: SIMULATION EXCERCISE

Let's investigate the exponential distribution and compare it with the Central Limit Theorem. The first step is to create a random data with the rexp function with lambda 0.2

```{r}
exp_data <- as.data.frame(replicate(40, mean(rexp(1000, 0.2))))
head(1/exp_data, 10)
```
Calculating the means of the 40 simulation of size 1000, we can see that all means are approximately 0.2. Let's compute the average of the 40 means

```{r}
mean_sample <- 1/mean(exp_data$`replicate(40, mean(rexp(1000, 0.2)))`)
round(mean_sample, 2)
```
The value 0.2 is the average of the 40 means calculated in the simulations rounding to 2 decimals, it is the expected value of theoretical mean.

Now we are going to check the standard desviation of the simulations

```{r}
exp_data_sd <- as.data.frame(replicate(40, sd(rexp(1000, 0.2))))
head(1/exp_data, 10)
```

```{r}
sd_sample <- 1/mean(exp_data_sd$`replicate(40, sd(rexp(1000, 0.2)))`)
round(mean_sample, 2)
```
As we see, the value of the standard deviations are approximately 0.2

Finally plot the histogram of a large simulations to show that it is close to a normal distribution

```{r}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40)))
hist(mns, main = 'Histogram for 40 simulations')
```

