---
title: "Regressions Models Practice"
author: "Robinson Andres Montes Gómez"
date: "11/16/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Is an automatic or manual transmission better for MPG?

The first step is to do summary of the variables

```{r cars}
summary(mtcars)
```

## Regression

Now let's start the regression analysis, with mpg as dependent variable and transmission (am) as independent variable. Beginning with the scatter plot and then with the regression analysis.

```{r}
scatter.smooth(x = mtcars$am, y = mtcars$mpg, main = 'Scatter Plot')
```

```{r}
fit <- lm(mpg ~ factor(am), mtcars)
summary(fit)
```
The 33.85% of the mpg is explained by the transmission, the other 66.15% depends of other variables. The model is statistical significant with a confidence level of 95% (p-value = 0.000285). According to the regression, a car with a manual transmission is more efficient than an automatic car, increasing the mpg in 7.245 miles/gallon.

## RESIDUAL DIAGNOSTIC

Plot of Residuals

```{r}
hist(fit$residuals,freq = FALSE,main = "Distribution Residuals")
```

QQ-Plot

```{r}
library(car)
qqPlot(fit$residuals)
```

There is statistical evidence that the residuals have a normal distribution.
